Consistency scores in text data

### 2020-07-23 outputs/documents/paper.Rmd
GPT write-ups in progress

The application of n-gram is versatile. N-gram is widely applied in text prediction, spelling-correction, machine translation. We use n-gram to [add how we use n-gram once the functions in the app are in place]

@@

In recent years, the use of pre-trained language models has played a significant role in advancing natural language processing (NLP) tasks such as reading comprehension, text generation, and **X** **(Ke-Li add ref)**. Pre-trained models remove the need for researchers to create training datasets or devote computational resources to this stage. Because of this, there has been substantial development in NLP research.

OpenAI's GPT-3 is a generative, pre-trained, task-agnostic, language model that was released by OpenAI in **Ke-Li add month** 2020 **(Ke-Li add ref)**. OpenAI is **(Ke-Li add background)**. GPT-3 is the **Ke-Li add number X** model publicly released by OpenAI. It has '175 billion parameters' and OpenAI claim that it as the 'capacity to generate text that ressembles human creation' **(Ke-Li add ref)**. Initial research has found... **(Ke-Li please find papers that use it, describe them, and add refs - look on arXiv)**. 
These parameters refer to the weights of the connections that enable the neural network to learn **(Keli add citation)**. GPT-3 can learn NLP tasks with few examples and without a task-specific dataset **(Keli add citation)**.

GPT-3 is pre-trained, and takes a sample of text as an input **(Ke-Li add more detail about what it needs and what it outputs and how it works).**. It adapts to the the style of the data that is used an input **(Ke-Li please find the language that they use for this and then we need to make ours consistent with theirs).**

>>>>

The application of n-gram is versatile. N-gram is widely applied in text prediction, spelling-correction, machine translation. In our application, we use a trigram-based model to detect both real-word and non-word errors and correct them with the candidate word that has the highest probability. [add more about how we use n-gram once the functions in the app are in place]

@@

In recent years, the use of pre-trained language models has played a significant role in advancing natural language processing (NLP) tasks such as reading comprehension, text generation, and even creative writing **(Ke-Li add ref)**. Pre-trained models remove the need for researchers to create training datasets or devote computational resources to this stage. Because of this, there has been substantial development in NLP research.

OpenAI's GPT-3 is a generative, pre-trained, task-agnostic, language model that was released by OpenAI in June 2020 **(Ke-Li add ref)**. OpenAI is an AI research company who openly pursues Artificial General Intelligence—to have machines learn and understand any intellectual tasks as human do **(Ke-Li add ref)**. GPT-3 is the third Generative Pre-trained Transformer language model publicly released by OpenAI. It has '175 billion parameters' and can learn NLP tasks with just a few examples. OpenAI claims that the text generation by GPT-3 is 'difficult for humans to distinguish from authentic human content' **(Ke-Li add ref)**. Since the API of GPT-3 at the moment is only available to a few invited users, public applications of GPT-3 are limited. On the other hand, its predecessor, GPT-2, has enabled researchers made breakthroughs in the past years. Alt, Hubner and Henning extended GPT-2 to relation extraction, which is a task of identifying the relationship between concepts appeared in text. They had shown a milestone in predicting larger range of distinct relation types with higher confidence **(Ke-Li add ref)**. In the field of speech recognition, data scarcity is often an issue due to the difficulty to collect large amount of data from human for learning **(Ke-Li add ref)**. Bird, Faria, Ekart, Premebida and Ayrosa employed GPT-2 as part of the solution to generate augmented data for classification. GPT-2 also helped NLP researchers tackling the task of textual paraphrasing **(Ke-Li add ref)**. Hedge and Patil used GPT-2 to build an unsupervised paraphrasing model that is not restricted by domain shift within an article, which is a problem faced by the usual supervised models of paraphrasing.  
**(Ke-Li please find papers that use it, describe them, and add refs - look on arXiv)**.

The above examples using GPT-2 were task-agnostic but they were in need of fine-tuning.
These parameters refer to the weights of the connections that enable the neural network to learn **(Keli add citation)**. GPT-3 can learn NLP tasks with few examples and without any task-specific dataset **(Keli add citation)**.

GPT-3 is pre-trained, and takes a sample of text as an input **(Ke-Li add more detail about what it needs and what it outputs and how it works).**. 
**(Ke-Li please find the language that they use for this and then we need to make ours consistent with theirs).**

Deep language representations, e.g. those
learned by the Transformer (Vaswani et al., 2017)
via language modeling (Radford et al., 2018),
have been shown to implicitly capture useful semantic and syntactic properties of text solely by
arXiv:1906.08646v1 [cs.CL] 19 Jun 2019
unsupervised pre-training (Peters et al., 2018)
